### 2019-11-20 Transfer_Learning/cvpr_submission/experiments.tex
Rearranging folders and references

\begin{figure*}[htb]
	\centering
	\begin{subfigure}{\textwidth}
		\centering
		\includegraphics[width=0.9\textwidth]{img/results/samnet_cog_orig_canonical_no_labels.png}
	\end{subfigure}%
	\newline
	\begin{subfigure}{\textwidth}
		\centering
		\includegraphics[width=0.9\textwidth]{img/results/samnet_cog_orig_hard.png}
	\end{subfigure}%
	\caption{Comparison of test set accuracies of SAMNet (blue) with original results achieved by the 
		baseline model~\cite{yang2018dataset} (gray) on Canonical (top) and Hard (bottom) variants of the COG dataset.}
	\label{fig:samnet_cog_detailed}
\end{figure*}

@@

\begin{figure}[!t]
	\centering
	\includegraphics[width=\columnwidth]{img/results/CoGenT_results.pdf}
	\caption{CLEVR-CoGenT accuracies for all tasks $t$ when training on $t$ only, training on all tasks jointly and training on all tasks but $t$.} %For all experiments, the validation and test sets are identical.
	\label{fig:CoGenT-results}
\end{figure}

@@

\begin{figure}[htb]
	\centering
	\includegraphics[width=\columnwidth]{img/architecture/hierarchy}
	\caption{Hierarchy of Task Groups.}
	\label{fig:task-groups}
\end{figure}

@@

\begin{figure}[!t]
	\centering
	\includegraphics[width=\columnwidth]{img/results/COG_reasoning_transfer_v3}
	\caption{COG accuracies for all task groups $t$ when training on $t$ only; training on Group A or B; and on all tasks.}
	\label{fig:COG-reasoning-results}
\end{figure}

@@

\begin{figure}[htb]
	\centering
	\includegraphics[width=\columnwidth]{img/results/samnet_cog_overall_transfer.png}
	\caption{Total accuracies of SAMNet (blue) and baseline models (light/dark gray) when testing generalization from Canonical to Hard variants of the dataset.}
	\label{fig:samnet_cog_overall_transfer}
\end{figure}

@@

\begin{figure}[!t]
	\centering
	\includegraphics[width=0.8\columnwidth]{img/results/CoGenT_B_results.pdf}
	\caption{Test accuracy on CoGenT-A \& -B when training on CoGenT-A (blue) and fine-tuning on CoGenT-B (gray).}
	\label{fig:CoGenT-B-results}
\end{figure}

>>>>

\begin{figure*}[htb]
	\centering
	\begin{subfigure}{\textwidth}
		\centering
		\includegraphics[width=0.9\textwidth]{../img/results/samnet_cog_orig_canonical_no_labels.png}
	\end{subfigure}%
	\newline
	\begin{subfigure}{\textwidth}
		\centering
		\includegraphics[width=0.9\textwidth]{../img/results/samnet_cog_orig_hard.png}
	\end{subfigure}%
	\caption{Comparison of test set accuracies of SAMNet (blue) with original results achieved by the 
		baseline model~\cite{yang2018dataset} (gray) on Canonical (top) and Hard (bottom) variants of the COG dataset.}
	\label{fig:samnet_cog_detailed}
\end{figure*}

@@

\begin{figure}[!t]
	\centering
	\includegraphics[width=\columnwidth]{../img/results/CoGenT_results.pdf}
	\caption{CLEVR-CoGenT accuracies for all tasks $t$ when training on $t$ only, training on all tasks jointly and training on all tasks but $t$.} %For all experiments, the validation and test sets are identical.
	\label{fig:CoGenT-results}
\end{figure}

@@

\begin{figure}[htb]
	\centering
	\includegraphics[width=\columnwidth]{../img/architecture/hierarchy}
	\caption{Hierarchy of Task Groups.}
	\label{fig:task-groups}
\end{figure}

@@

\begin{figure}[!t]
	\centering
	\includegraphics[width=\columnwidth]{../img/results/COG_reasoning_transfer_v3}
	\caption{COG accuracies for all task groups $t$ when training on $t$ only; training on Group A or B; and on all tasks.}
	\label{fig:COG-reasoning-results}
\end{figure}

@@

\begin{figure}[htb]
	\centering
	\includegraphics[width=\columnwidth]{../img/results/samnet_cog_overall_transfer.png}
	\caption{Total accuracies of SAMNet (blue) and baseline models (light/dark gray) when testing generalization from Canonical to Hard variants of the dataset.}
	\label{fig:samnet_cog_overall_transfer}
\end{figure}

@@

\begin{figure}[!t]
	\centering
	\includegraphics[width=0.8\columnwidth]{../img/results/CoGenT_B_results.pdf}
	\caption{Test accuracy on CoGenT-A \& -B when training on CoGenT-A (blue) and fine-tuning on CoGenT-B (gray).}
	\label{fig:CoGenT-B-results}
\end{figure}
